---
title: "Designing a new supermarket"
author: "Sarah Marshall"
date: "`r Sys.Date()`"
output: html_document
---


```{r, echo = FALSE, results = "hide"}
###########################################
#### EDIT NUMBERS IN THIS SECTION #########
###########################################
simulation_length = 10000  # number of minutes

policy = "shortest-queue" # how do customers join the queue
#policy = "random"
###########################################
```





```{r, echo = FALSE, results = "hide"}
lambda_express = 4               # number of customers arriving per minute
lambda_regular = 1              # number of customers arriving per minute

average_service_time_express = 1 # number of minutes
average_service_time_regular = 5 # number of minutes

mu_express = 1/average_service_time_express
mu_regular = 1/average_service_time_regular

```




```{r setup, include=FALSE, message = FALSE}
packages_needed <- c("tidyverse", "flexdashboard", 
                     "simmer","simmer.plot",
                     "plotrix", "grDevices", "xtable",
                     "kableExtra")

packages_to_install <- packages_needed[!packages_needed %in%
                                         installed.packages()]
sapply(packages_to_install, install.packages,
       dependencies=TRUE, repos="https://cloud.r-project.org")
sapply(packages_needed, require, character=TRUE)

knitr::opts_chunk$set(echo = FALSE, 
                      results = "hide", 
                      message = FALSE)


show_theory = FALSE

source("Code/queueing_functions.R")
```



### **Summary of parameters**



* Express Customers 
  - Arrival rate, $\lambda$ = `r lambda_express` per minute
  - Service rate, $\mu$ = `r mu_express` per minute
* Regular Customers 
  - Arrival rate, $\lambda$ = `r lambda_regular` per minute
  - Service rate, $\mu$ = `r mu_regular` per minute

* Simulation length = `r simulation_length` minutes `r simulation_length/60` hours


```{r, eval = FALSE}
# run simulation
nreps = 50
summary_df <- expand_grid(num_self = c(0, 4:10), num_staff = 6:7, j = 1:nreps)
summary_df <- summary_df %>% mutate(
  cost = 10*num_self + 100*num_staff,
  Wq_Exp = NA*0,
  Wq_Reg = NA*0,
  Wq_All = NA*0,
) %>%filter(cost <=700, cost > 600)

for(i in 1:dim(summary_df)[1]){
  print(i)
mmc.env <- run_simulation_checkouts(lambda_express,
                                    lambda_regular,
                                    mu_express,
                                    mu_regular,
                                    num_servers_selfcheckout=summary_df[i,"num_self"] %>%pull(),
                                    num_servers_staffed=summary_df[i,"num_staff"]%>%pull(),
                                    simulation_length=simulation_length,
                                    policy = policy)
q <- plot_number_in_queue(mmc.env, num_per_row=3)
q <- get_performance_checkouts(mmc.env, q)
summary_df[i,5:7] <- t(q$results$Wq_sim)
}

write_csv(summary_df, paste0("output/simulation_output_", simulation_length, "_", nreps, ".csv"))
```


```{r}
summary_df = read_csv("output/simulation_output_10000_50.csv")
nreps = max(summary_df$j)
```

### **Simulation Results**

* Number of simulation runs = `r nreps`


```{r summarise_results1, results = "asis"}

summary_df <- summary_df %>% mutate(id = row_number())


# create summary table
summary_table <- summary_df %>% group_by(num_self, num_staff) %>% 
  summarise(
    cost = unique(cost),
    Wq_Exp_mean = mean(Wq_Exp),
    Wq_Reg_mean = mean(Wq_Reg),
    Wq_Exp_probg1 = sum(Wq_Exp>1)/nreps,
    #Wq_Exp_probl1 = sum(Wq_Exp<1)/nreps,
    Wq_Reg_probg5 = sum(Wq_Reg>5)/nreps
    
  )

kable(summary_table, "html") %>%
  kable_styling(full_width = F)

```



```{r summarise_results2}

# Create long table for plot
summary_df_long <- summary_df %>% pivot_longer(cols = starts_with("Wq"), values_to = "Wq", names_to = "CustomerType") %>% 
  mutate(CustomerType = str_replace(CustomerType, "Wq_", ""),
         CustomerType = str_replace(CustomerType, "Exp", "Express"),
        CustomerType = str_replace(CustomerType, "Reg", "Regular"))


summary_df_long_table <- summary_df_long %>%  group_by(num_self, num_staff, CustomerType) %>% 
  summarise(
    cost = mean(cost),
    mean = mean(Wq),
    min = min(Wq),
    max = max(Wq),
    probg1 = sum(Wq>1)/nreps,
    #Wq_Exp_probl1 = sum(Wq_Exp<1)/nreps,
    probg5 = sum(Wq>5)/nreps,
    .groups = "keep"
    
  ) %>% filter(num_staff<7) %>% mutate(Ws = case_when(CustomerType=="Express" ~ average_service_time_express,
                              CustomerType=="Regular" ~average_service_time_regular,
                              TRUE ~ NA)) %>% 
  ungroup() %>% group_by(CustomerType) %>%
  mutate(
  group_max = max(max)
               )
  
               
temp <- summary_df_long_table %>% pivot_longer(cols=any_of(c("Ws", "mean", "min", "max")), names_to = "Type", values_to = "value") %>% filter(CustomerType!="All")
```

```{r histogram, fig.height = 12, fig.width = 8, out.width = "100%"}
summary_df_long %>% filter(CustomerType != "All", num_staff < 7) %>% ggplot() + geom_histogram(aes(x=Wq), bins=20) +
  facet_grid(rows=vars(num_self, num_staff), cols =vars(CustomerType), scales = "free", labeller = label_both)+
  labs(x = "Expected time in queue", y = "Frequency", 
       title = paste0("Expected waiting time by customer type for different configurations\nn=", nreps, " simulation runs"),
       )+# xlim(0, 20)+
  geom_vline(mapping=aes(xintercept =value, col = Type#, lty=Type
                         ), linewidth=1.5, data = temp %>%filter(Type%in%c("mean", "Ws"), num_staff < 7))+
  geom_text(mapping = aes(x = group_max, y = 5, label = paste0("$",cost)), data = summary_df_long_table %>% filter(CustomerType!="All", num_staff < 7) )

```


