---
title: "Modelling Queues"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---



```{r, echo = FALSE, results = "hide"}
###########################################
#### EDIT NUMBERS IN THIS SECTION #########
###########################################

lambda = 1                 # number of customers arriving per minute
mu = 2                     # number of customers served per minute
num_servers = 2            # number of checkout operators
simulation_length = 100     # number of minutes


average_service_time = 1/mu  # number of minutes 
rho = lambda/(mu*num_servers)# traffic intensity

###########################################
```





```{r setup, include=FALSE, message = FALSE}
packages_needed <- c("tidyverse", "flexdashboard", 
                     "simmer","simmer.plot",
                     "plotrix", "grDevices", 
                     "kableExtra")

packages_to_install <- packages_needed[!packages_needed %in%
                                         installed.packages()]
sapply(packages_to_install, install.packages,
       dependencies=TRUE, repos="https://cloud.r-project.org")
sapply(packages_needed, require, character=TRUE)

knitr::opts_chunk$set(echo = FALSE, 
                      results = "hide", 
                      message = FALSE)

source("Code/queueing_functions.R")
show_theory = FALSE
```






A single queue with $n$ servers
=====================================  
Row {data-height=250}
-----------------------------------------------------------------------
### **Summary of parameters**

```{r}
type_of_queue = "one_line"
```

* Arrival rate, $\lambda$ = `r lambda` per minute
* Service rate, $\mu$ = `r mu` per minute
* Number of servers, $n$= `r num_servers`
* Type of queue = `r type_of_queue`
* Length of simulation = $`r simulation_length`$ min = $`r round(simulation_length/60, 2)`$ hours
* Traffic intensity, $\rho$ = $`r rho`$ 

### **Queue Layout**

```{r, fig.dim = c(7, 4)}
plot_queue_layout(num_servers, type_of_queue)

```


 
```{r runsim1, echo = FALSE, results = "hide"}
# Run simulation
mmc.env <-run_simulation(lambda, mu, num_servers, 
                         simulation_length, 
                         type_of_queue = type_of_queue)
```


Row {data-height=400}
-----------------------------------------------------------------------
### **Number in the queue**

```{r plotsim1, fig.dim = c(12, 4)}
q <- plot_number_in_queue(mmc.env)
q$graph
```


Row {data-height=350}
-----------------------------------------------------------------------
### **Performance Measures**
```{r perform1, results = "asis"}
q <- get_performance(mmc.env, q, include_theory = show_theory,
                             lambda, mu, num_servers, type_of_queue)

print_table(q,include_theory = show_theory)
```


$n$ queues with $n$ servers {data-orientation=rows}
=====================================  


```{r}
type_of_queue = "individual_lines"
policy = "random"
#policy = "shortest-queue"

```

Row {data-height=250}
-----------------------------------------------------------------------
### **Summary of parameters**

* Arrival rate, $\lambda$ = `r lambda` per minute
* Service rate, $\mu$ = `r mu` per minute
* Number of servers, $n$= `r num_servers`
* Type of queue = `r type_of_queue`
* Length of simulation = $`r simulation_length`$ min = $`r round(simulation_length/60, 2)`$ hours
* Traffic intensity, $\rho$ = $`r rho`$ 


### **Queue Layout**

```{r, fig.dim = c(7, 4)}
plot_queue_layout(num_servers, type_of_queue)

```


 


```{r, echo = FALSE, results = "hide"}
# Run simulation
mmc.env <-run_simulation(lambda, mu, num_servers, 
                         simulation_length, 
                         type_of_queue = type_of_queue,
                         policy =  policy)
```


 

Row {data-height=400}
-----------------------------------------------------------------------
### **Number in the queue**

```{r, fig.dim = c(12, 4)}
q <- plot_number_in_queue(mmc.env)
q$graph
```


Row {data-height=350}
-----------------------------------------------------------------------

### **Performance Measures**
```{r, results = "asis"}
q = get_performance(mmc.env, q, include_theory = show_theory,
                             lambda, mu, num_servers, type_of_queue)

print_table(q,include_theory = show_theory)
```




