```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      results = "hide", 
                      message = FALSE)
                      
## no need to load libraries
## as these are part of the codesharey3 package

## code from queueing_functions.R

run_simulation <- function(
    lambda, mu, num_servers, simulation_length, type_of_queue,
    policy = "random"){

  if(type_of_queue == "one_line"){
    # Define queue
    mmc.trajectory <- trajectory() %>%
      seize("checkouts", amount=1) %>%
      timeout(function() rexp(1, mu)) %>%
      release("checkouts", amount=1)

    #Run simulation
    mmc_env <- simmer() %>%
      add_resource("checkouts", capacity=num_servers, queue_size=Inf) %>%
      add_generator("Customer", mmc.trajectory,
                    function() rexp(1, lambda)) %>%
      run(until=simulation_length)

    return(mmc_env)



  }else if(type_of_queue == "individual_lines"){

    server_names <-    paste0("checkout", ifelse(num_servers>=10 & 1:num_servers < 10,
                                                 "0", ""),
                              1:num_servers)

    mmc.trajectory <-
      trajectory("Customer's path") %>%
      set_attribute("start_time", function() {now(mmc_env)}) %>%
      select(server_names, policy = policy) %>%
      seize_selected() %>%
      timeout(function() {rexp(1, mu)}) %>%
      release_selected()

    mmc_env <-
      simmer("mmc_env")

    for(i in 1:num_servers){
      mmc_env <- mmc_env %>% add_resource(server_names[i])
    }
    mmc_env <- mmc_env %>%
      add_generator("Customer", mmc.trajectory, function() rexp(1, lambda))

    mmc_env <- mmc_env %>%
      run(until=simulation_length)

    return(mmc_env)
  }


}

plot_queue_layout <- function( num_servers, type_of_queue){

  par(mar=c(5.1, 4.1, 4.1, 2.1)-c(5,4,4,2))

  plot(c(0, 100), c(0, 100), type= "n", xlab = "", ylab = "", axes = FALSE)

  height = 10
  mylwd = 2

  if(type_of_queue == "one_line"){
    num_queues = 1

      # Draw queue
    if(num_queues==1){
      queues_y_pos = c(40)
      rect(0, 40, 40, 60, lwd =mylwd)

      # Draw service
      rect(60, 10, 80, 90, lwd = mylwd)
      arrows(45, 50, 55, 50, length = 0.15, lwd = mylwd)
      servers_y_pos = (80/(num_servers+1))*(c(1:num_servers))+10
      for(i in 1:num_servers){
        draw.circle(70, servers_y_pos[i], height/4, lwd = mylwd)
        arrows(85, servers_y_pos[i], 95, servers_y_pos[i], length = 0.15, lwd = mylwd)
      }
    }


 }else if(type_of_queue == "individual_lines"){
    num_queues = num_servers

    queues_y_pos = (100/(num_queues+1))*(c(1:num_queues))


    for(i in 1:num_queues){
      rect(0, queues_y_pos[i]-height/2, 40, queues_y_pos[i]+height/2, lwd = mylwd)

      # text(seq(5, 35, 5),  queues_y_pos[i], labels=emoji(emoji_queue), cex=emoji_size, #col='steelblue',
      #     family='EmojiOne')


      arrows(45, queues_y_pos[i], 55, queues_y_pos[i], length = 0.15, lwd = mylwd)
      servers_y_pos <- queues_y_pos
      rect(60, servers_y_pos[i]-height/2, 80, servers_y_pos[i]+height/2, lwd = mylwd)

      for(i in 1:num_servers){
        draw.circle(70, servers_y_pos[i], height/4, lwd = mylwd)
        arrows(85, servers_y_pos[i], 95, servers_y_pos[i], length = 0.15, lwd = mylwd)
      }


    }

  }
}


plot_number_in_queue <- function(env, print_theory = FALSE, text_size=20,
                                 num_per_row = 4){
  mmc.mon <- get_mon_resources(env)
  graph <- plot(mmc.mon,
                metric = "usage",
                #names = server_names",
                items =  c("system", "server", "queue"),
                steps = FALSE)+ theme(text = element_text(size = text_size))

  if(print_theory){
    graph <- graph + geom_hline(aes(yintercept = Number, colour = Item),
                                data = theory, #data
                                alpha = 0.4, #transperancy
                                size = 2  #line width
    )  + annotate("text",
                  x = now(env)*c(0.95, 1, 0.95),
                  y = theory$Number,
                  label = c("L", "L[s]", "L[q]"),
                  parse=TRUE)
  }

  if(length(env$resources) >num_per_row){
    graph <- graph + facet_wrap(~resource, ncol = num_per_row)
  }

  return(list(mmc.mon = mmc.mon, graph = graph))
}



get_performance <- function(mmc.env, q, include_theory,
                            lambda, mu, num_servers, type_of_queue){

  graph <- q$graph

  L_sim_est <- graph$data %>%
    group_by(item, resource) %>%
    summarise(n = n(),
              L_est_resource = mean[n]) %>%
    group_by(item) %>%
    summarise(L_est = sum(L_est_resource))


  mmc.arrivals <- get_mon_arrivals(mmc.env) %>%
    mutate(
      t_system = end_time - start_time,
      t_queue = t_system-activity_time,
      t_service = activity_time,
      service_start_time = end_time - activity_time) %>%
    arrange(start_time)
    #left_join(mmc.mon, by = c("start_time" = "time")) %>%
    #mutate(CustomerType = substr(name, 1, 11))



  W_sim <- mean(mmc.arrivals$t_system)
  Wq_sim <- mean(mmc.arrivals$t_queue)
  Ws_sim <- mean(mmc.arrivals$t_service)
  mu_sim <- 1/Ws_sim
  lambda_sim <- 1/mean(diff(c(0, (mmc.arrivals$start_time))))

  results <- tibble(
    Name = c("Arrival Rate", "Service Rate",
             "Number in System", "Number in Service", "Number in Queue",
             "Time in System", "Time in Service", "Time in Queue"),
    Symbol = c("lambda", "mu",  "L", "L_s", "L_q", "W", "W_s", "W_q"),
    Simulation = c(lambda_sim, mu_sim,
                   as.numeric(L_sim_est$L_est),
                   W_sim, Ws_sim, Wq_sim),
  )

  if(include_theory){
    results <-mutate(results,
                     Theory =  compute_theory(lambda, mu, num_servers, type_of_queue),
                     Difference = Theory - Simulation
    )
  }

  q$mmc.arrivals = mmc.arrivals
  q$results = results
  return(q)
}


get_performance_checkouts <- function(mmc.env, q){

    graph <- q$graph

    L_sim_est_resource <- graph$data %>%
      group_by(item, resource) %>%
      summarise(n = n(),
                L_est_resource = mean[n])


    L_sim_est_resource_type <-  graph$data %>%
      mutate(resourceType= substr(resource, 1, 4)) %>%
      group_by(item, resourceType) %>%
      summarise(n = n(),
                L_est_resource = mean[n])


    L_sim_est_total <-L_sim_est_resource  %>%
            group_by(item) %>%
      summarise(L_est = sum(L_est_resource))

    mmc.arrivals <- get_mon_arrivals(mmc.env) %>%
      mutate(
        t_system = end_time - start_time,
        t_queue = t_system-activity_time,
        t_service = activity_time,
        service_start_time = end_time - activity_time,
        CustomerType = substr(name, 1, 11)
        ) %>%
      arrange(start_time)
    #%>%    left_join(mmc.mon, by = c("start_time" = "time"))



  mmc.arr.sum <- mmc.arrivals %>%
    group_by(CustomerType) %>%
    mutate(
      lambda_diff = start_time - lag(start_time)
    ) %>%
    summarise(
      W_sim = mean(t_system),
      Wq_sim = mean(t_queue),
      Ws_sim = mean(t_service),
      mu_sim = 1/Ws_sim,
      lambda_sim = 1/mean(lambda_diff, na.rm=TRUE)
    ) %>% bind_rows(
    mmc.arrivals %>%
    summarise(
      W_sim = mean(t_system),
      Wq_sim = mean(t_queue),
      Ws_sim = mean(t_service),
      mu_sim = 1/Ws_sim,
      lambda_sim = 1/mean(start_time - lag(start_time), na.rm=TRUE)
    )
    )
  mmc.arr.sum[3,1] = "AllCustomers"
  #mmc.arr.sum <- mmc.arr.sum[, 1:2]
  #L_sim_est_resource_type %>% arrange(resourceType)
  q$mmc.arrivals = mmc.arrivals


  q$results = mmc.arr.sum
  return(q)


}


compute_theory <- function( lambda, mu, num_servers, type_of_queue){
  theory <- rep(NA, 8)
  if(type_of_queue=="one_line"){
    rho <- lambda/(mu*num_servers)
    rho

    i <- 0:(num_servers-1)
    pi0 <- 1/(sum((num_servers*rho)^i/factorial(i)) +
                (num_servers*rho)^num_servers/(factorial(num_servers)*(1-rho)))
    pi0

    #Theoretical Values
    Ls <-lambda/mu
    Lq <- pi0*(num_servers*rho)^num_servers*rho/
      (factorial(num_servers)*(1-rho)^2)
    L <-  pi0*(num_servers*rho)^num_servers*rho/
      (factorial(num_servers)*(1-rho)^2) + Ls
    Ws <- 1/mu
    Wq <- Lq/lambda
    W <- L/lambda

    theory <- c(lambda, mu,  L, Ls, Lq, W, Ws, Wq)
  }else if(type_of_queue=="individual_lines"){

    #Theoretical Values M/M/1 with multiple lines
    lambda_ind  <- lambda/num_servers
    rho <- lambda_ind/mu
    L  <- rho/(1-rho)
    Ls <- rho
    Lq <- rho^2/(1-rho)
    W  <- L/lambda_ind
    Ws <- 1/mu
    Wq <- rho/(mu-lambda_ind)
    Var_L <- rho/(1-rho)^2
    Var_W <- 1/((1-rho)^2*mu^2)


    theory <- c(lambda, mu,  L*num_servers, Ls*num_servers, Lq*num_servers,
                W, Ws, Wq)
  }

  return(theory)
}


print_table <- function(q, include_theory){
  tab <-  kable(q$results)%>%
    column_spec(1, width = "10em") %>%
    column_spec(2, width = "1em") %>%
    column_spec(3, width = "10em") #%>% #kable_material_dark() %>%
  #kable_styling(bootstrap_options = "striped")

  if(include_theory){
    tab <-  tab %>%   column_spec(4, width = "10em")%>%
      column_spec(5, width = "10em")
  }
  return(tab)

}

print_table_checkouts <- function(q, include_theory, comparison=NULL){
  temp <-  q$results[,c(1,3)]
  if(!is.null(comparison)) {
    temp <- cbind(temp, `Average Service Time`=comparison)
  }
  colnames(temp)[2] = "Average Time in Queue (sim)"
  tab <-  kable(temp)%>%
     column_spec(1, width = "10em") %>%
     column_spec(2, width = "10em")
  if(!is.null(comparison)) {
    tab <- tab %>%
     column_spec(3, width = "10em")
  }
    # column_spec(4, width = "10em")#%>%
    # column_spec(5, width = "10em")%>%
    # column_spec(6, width = "10em")

  return(tab)
}


```

```{r, echo = FALSE, results = "hide"}
# settings for this run
show_theory = FALSE
```

::: col-xs-6

:::: row
## A single queue with $n$ servers

::: col-xs-6
### **Summary of parameters**

```{r}
type_of_queue = "one_line"
average_service_time = 1/mu   # number of minutes 
rho = lambda/(mu*num_servers) # traffic intensity
```

* Arrival rate, $\lambda$ = `r lambda` per minute
* Service rate, $\mu$ = `r mu` per minute
* Number of servers, $n$ = `r num_servers`
* Type of queue = `r type_of_queue`
* Length of simulation = $`r simulation_length`$ min = $`r round(simulation_length/60, 2)`$ hours
* Traffic intensity, $\rho$ = $`r rho`$ 
:::

::: col-xs-6
### **Queue Layout**

```{r, fig.dim = c(7, 4)}
plot_queue_layout(num_servers, type_of_queue)

```
:::


```{r, echo = FALSE, results = "hide"}
# Run simulation
mmc.env <-run_simulation(lambda, mu, num_servers, 
                         simulation_length, 
                         type_of_queue = type_of_queue)
```


::: col-xs-12
### **Number in the queue**

```{r, fig.dim = c(12, 4)}
q <- plot_number_in_queue(mmc.env)
q$graph
```
:::


::: col-xs-6
### **Performance Measures**
```{r, results = "asis"}
q <- get_performance(mmc.env, q, include_theory = show_theory,
                             lambda, mu, num_servers, type_of_queue)

print_table(q,include_theory = show_theory)
```
:::
::::

:::

::: col-xs-6

:::: row
## $n$ queues with $n$ servers {data-orientation=rows}


```{r}
type_of_queue = "individual_lines"
policy = "random"
#policy = "shortest-queue"
average_service_time = 1/mu   # number of minutes 
rho = lambda/(mu*1) # traffic intensity
```

::: col-xs-6
### **Summary of parameters**

* Arrival rate, $\lambda$ = `r lambda` per minute
* Service rate, $\mu$ = `r mu` per minute
* Number of servers, $n$ = `r num_servers`
* Type of queue = `r type_of_queue`
* Length of simulation = $`r simulation_length`$ min = $`r round(simulation_length/60, 2)`$ hours
* Traffic intensity, $\rho$ = $`r rho`$ 

:::

::: col-xs-6

### **Queue Layout**

```{r, fig.dim = c(7, 4)}
plot_queue_layout(num_servers, type_of_queue)

```
:::

```{r, echo = FALSE, results = "hide"}
# Run simulation
mmc.env <-run_simulation(lambda, mu, num_servers, 
                         simulation_length, 
                         type_of_queue = type_of_queue,
                         policy =  policy)
```


::: col-xs-12
### **Number in the queue**

```{r, fig.dim = c(12, 4)}
q <- plot_number_in_queue(mmc.env)
q$graph
```
:::

::: col-xs-6
### **Performance Measures**
```{r, results = "asis"}
q = get_performance(mmc.env, q, include_theory = show_theory,
                             lambda, mu, num_servers, type_of_queue)

print_table(q,include_theory = show_theory)
```
:::
::::

:::
